Extending the WebID Protocol with Access Delegation

### 2012-08-04 paper.tex

@@

\lstinputlisting[
    lastline=36,name=views,style=turtle,float=htb,label=listing:views,
    basicstyle=\ttfamily\scriptsize,
    caption={Views on Juliet's FOAF profile by Freedom Box Laurence, when acting as Romeo and when acting as Lord Montague }
]{Listings/views.n3}

\subsubsection{TLS inefficiency: }

>>>>

But when the origin server $OS$ is serving a number of different profiles $P_1 \ldots P_n$ each identifying the N users $U_1 \ldots U_n$ and is acting on behalf of a these users, as would be the case for a company, government agency, school, educational instituion, charyity, football club, ... server, then we have two issues that need to be taken into account: first an issue of data perspective and an efficiency issue.

@@

\lstinputlisting[
    lastline=36,name=views,style=turtle,float=htb,label=listing:views,
    basicstyle=\ttfamily\scriptsize,
    caption={Views on Juliet's FOAF profile by Freedom Box Laurence, when acting as Romeo and when acting as Lord Montague }
]{Listings/views.n3}\todo{ST: \autoref{listing:views} is too long (maybe shorten, I dont know)}
